\Large \bf Uncovering Bugs in Distributed Storage Systems\\during Testing (not in Production!)

### 2015-09-22 experience.tex
minor updates in case studies

\subsection{Live \Azure Table Migration}
\label{sec:cases:migration}

The Live \Azure Table Migration library (MigratingTable) is designed to transparently migrate a data set between tables in an \Azure Storage service while an application is accessing this data set. This case study is particularly interesting because its developers \emph{co-developed} the system with its \psharp test to increase confidence in the system. Indeed, this co-development process resulted in the discovery of several tricky bugs before the system went into production (see \S\ref{sec:eval}). The MigratingTable testing effort differs from the vNext case study: the vNext developers focused on specifying a single liveness property, while the MigratingTable test checks complete compliance with an interface specification.

@@

MigratingTable provides a \emph{virtual table} that has a similar interface to an ordinary \Azure table. This interface is named \texttt{IChainTable}. The virtual table is backed by a pair of \emph{old} and \emph{new} tables, which must also implement \texttt{IChainTable}. A background \emph{migrator} job is responsible for moving all data from the old table to the new table. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which is intended to guarantee that when multiple application processes issue \emph{input} operations to their own MigratingTable instances with the same backend tables, the output of the MigratingTable instances is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of the \psharp test was to verify this property.

>>>>

\subsection{Live Table Migration}
%\subsection{Live \Azure Table Migration}
\label{sec:cases:migration}

The Live Table Migration library (MigratingTable) is designed to \emph{transparently} migrate a data set between tables in a
%The Live \Azure Table Migration library (MigratingTable) is designed to \emph{transparently} migrate a data set between tables in an
\Azure Storage service \emph{while} an application is accessing this data set. This case study is particularly interesting because its developers \emph{co-developed} the system with its \psharp test harness to increase confidence in the system. Indeed, this co-development process resulted in the discovery of several tricky bugs before the system went into production (see \S\ref{sec:eval}). The MigratingTable testing effort differs from the vNext case study: the vNext developers focused on specifying a single liveness property, while the MigratingTable test checks complete compliance with an interface (safety) specification.

@@

MigratingTable provides a \emph{virtual table} that has the same interface as an ordinary \Azure table. This interface is named \texttt{IChainTable}. The virtual table is backed by a pair of \emph{old} and \emph{new} tables, which must implement \texttt{IChainTable}. A background \emph{migrator} job is responsible for transparently moving all data from the old table to the new table. Meanwhile, each read and write operation issued to the virtual table is translated to a sequence of reads and writes on the backend tables according to a protocol, which is intended to guarantee that when multiple application processes issue \emph{input} operations to their own MigratingTable instances with the same backend tables, the output of the MigratingTable instances is compliant with the specification of \texttt{IChainTable} for the combined \emph{input history} as if all the operations were done on a single table. The goal of using \psharp was to systematically test this property.
